A meta-analysis of mental rotation ability in the first years of life

### 2022-04-25 code/analysis.Rmd
Add column headers and halfeye to forest plot

```{r, fig_forest}
# Forest plot inputs
level <- 0.05
ndraws <- 1000

# Helper function for printing confidence intervals
print_num <- function(x) format(round(x, 2), trim = TRUE, nsmall = 2)
print_ci <- function(est, lb, ub) {
  paste0(print_num(est), " [", print_num(lb), ", ", print_num(ub), "]")
}

# Get draws from the Bayesian posterior distribution
draws <- epred_draws(res_brm, dat, ndraws = ndraws)
meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = ndraws) %>%
  mutate(article = "Three-level model", experiment = "zzz") # For the last line

# Create forest plot
dat %>%
  # Compute frequentist confidence intervals
  mutate(
    ci_lb = gi - qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    fontface = "plain" # For study labels and confidence interval
  ) %>%
  # Add meta-analytic effect size + CI
  bind_rows(list(
    article = "Three-level model",
    group = "",
    experiment = "zzz", # Just so it's displayed as the last line
    gi = res_ml$b,
    ci_lb = res_ml$ci.lb,
    ci_ub = res_ml$ci.ub,
    fontface = "bold"
  )) %>%
  # Format effect size + CI for printing them on the plot
  mutate(ci_print = print_ci(gi, ci_lb, ci_ub)) %>%
  # Reverse order of experiments so they are plotted alphabetically
  mutate(experiment = forcats::fct_rev(factor(experiment))) %>%
  arrange(experiment) %>%
  # Show article labels only for the first experiment per article
  mutate(
    article = if_else(article == lead(article, default = ""), "", article)
  ) %>%
  # Prepare plot
  ggplot(aes(x = gi, y = experiment)) +
  geom_vline(xintercept = seq(-1, 2, 1), size = 0.8, color = "grey90") +
  geom_vline(xintercept = seq(-1.5, 2.5, 1), size = 0.4, color = "grey90") +
  # Add article and group labels as text to the left
  geom_text(aes(x = -5.6, label = article, fontface = fontface), hjust = 0) +
  geom_text(aes(x = -3.1, label = group, fontface = fontface), hjust = 0) +
  # Add experiment specific effect size + CI as text to the right
  geom_text(aes(x = 4.4, label = ci_print, fontface = fontface), hjust = 1) +
  # Add Bayesian highest posterior density interval in the background
  stat_interval(aes(x = .epred), draws, point_interval = "mean_hdi") +
  stat_interval(aes(x = b_Intercept), meta_draws, point_interval = "mean_hdi") +
  # Add study specific effect size + CIs on top
  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
  # Add meta-analytic effect size as a line
  annotate("segment", x = res_ml$b, xend = res_ml$b, y = 0.7, yend = 1.3) +
  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
  scale_color_grey(
    start = 0.9, end = 0.6,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "Bayesian HPDI"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.584),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

>>>>

```{r, fig_forest}
# Forest plot inputs
level <- 0.05
n_draws <- 10000
n_experiments <- length(unique(dat$experiment))

# Helper functions for printing confidence intervals
print_num <- function(x) format(round(x, 2), trim = TRUE, nsmall = 2)
print_ci <- function(est, lb, ub) {
  paste0(print_num(est), " [", print_num(lb), ", ", print_num(ub), "]")
}

# Get posterior draws for each experiment
draws <- epred_draws(res_brm, dat, ndraws = n_draws) %>%
  mutate(experiment_f = factor(experiment))

# Get posterior draws for the meta-analytic effect
meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = n_draws)
meta_effect_size <- summary(res_brm)$fixed

# Create forest plot
dat %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-1, 2, 1), size = 0.8, color = "grey90") +
  geom_vline(xintercept = seq(-1.5, 2.5, 1), size = 0.4, color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -5.6, label = article), hjust = 0) +
  geom_text(aes(x = -3.1, label = group), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 4.4, label = ci_print), hjust = 1) +
  # Add Bayesian highest posterior density intervals for each experiment
  stat_interval(aes(x = .epred), draws, point_interval = "mean_hdi") +
  scale_color_grey(
    start = 0.9, end = 0.6,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = b_Intercept, y = -1),
    meta_draws,
    point_interval = "mean_hdi"
  ) +
  annotate(
    "text",
    x = -5.6,
    y = -0.5,
    label = "Three-level model",
    hjust = 0,
    fontface = "bold"
  ) +
  annotate(
    "text",
    x = 4.4,
    y = -0.5,
    label = print_ci(
      meta_effect_size$Estimate,
      meta_effect_size$`l-95% CI`,
      meta_effect_size$`u-95% CI`
    ),
    hjust = 1,
    fontface = "bold"
  ) +
  # Add headers for each of the for columns
  annotate( # Just to make the grid lines disappear
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-5.6, -3.1, 0, 4.4),
    y = n_experiments + 1.5,
    label = c(
      "Article", "Experiment", "Effect size plot", "Effect size statistic"
    ),
    hjust = c(0, 0, 0.5, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(ylim = c(-1.5, n_experiments + 2), expand = FALSE) +
  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "Bayesian HPDI"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.565),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )
